Stage-Splitting a Modal Language

### 2014-07-30 paper/splitting.tex
added theorems
started to expand definition of equiv (it's clever); going home
some additions to metatheory of splitting

>>>>

\subsection{Value Splitting, Etc}

...

\subsection{Metatheory}

We start with two careful definitions of equivalence ($\equiv$ on terms below, $\sim$ on values in \ref{fig:auxSplit}).  They are mutually dependent.

There are two problems with these definitions:
\begin{enumerate}
\item I'm not sure how to encode $\equiv$ with relations, since the iff requires inversion rather than direct derivation.
\item In the rule labeled PROBLEM, I have a sudden turnstile out of nowhere.  
  What I'm trying to say with that premise is ``for any equivalent arguments, the bodies are equivalent".
\end{enumerate}

\begin{definition}
For residuals $q$ and $r$, define $q \equiv r : A$ to mean that 
$e_1 \tworedsym v_1$ iff $\reduce {e_2} {v_2}$ where $v_1 \sim v_2 : A$
\end{definition}

All I'm trying to say here is that two terms are equivalent if they evaluate to the same value,
where "same" for functions means that those functions always evaluate to the same thing.

We give the following end-to-end correctness lemmas for closed terms (open term versions forthcoming).

\begin{lemma}
If $\cdot\vdash e : A \splittwosym [p,l.r]$ then,
\begin{itemize}
\item $\cdot \vdash e : A~@~\bbtwo$ 
\item $\diatwo [\cdot] e q$ iff $\reduce p u$ where
\item $q \equiv (\letin{l}{u}{r})$
\end{itemize}
\end{lemma}

\begin{lemma}
If $\cdot\vdash e : A \splitonesym [c,l.r]$ then,
\begin{itemize}
\item $\typesone [\cdot] e A$ 
\item $\diaone [\cdot] e {\xi;v}$ iff $\reduce c {(v_1,u)}$ where
\item $\dom \xi \vdash v \vsplito [v_1,v_2]$
\item $\reify \xi {v_2} q$
\item $q \equiv (\letin{l}{u}{r})$
\end{itemize}
\end{lemma}

%
%\subsubsection{Simple Types}
%
%\begin{theorem}
%If $\cdot\vdash e : A \splittwosym [p,l:\tau.r]$ then,
%\begin{itemize}
%\item $\cdot \vdash e : A~@~\bbtwo$ 
%\item $\types [\cdot] p \tau$ and $\types [l:\tau] r A$ 
%\item $\diatwo [\cdot] e q$ iff $\reduce p u$ and if so
%\item $q \equiv (\letin{l}{u}{r})$
%\end{itemize}
%\end{theorem}
%
%\begin{theorem}
%If $\cdot\vdash e : A \splitonesym [c,l:\tau.r]$ then,
%\begin{itemize}
%\item $\typesone [\cdot] e A$ 
%\item $A \tsplito [A_1,A_2]$
%\item $\types [\cdot] c {A_1 \times \tau}$ and $\types [l:\tau] r A_2$ 
%\item $\diaone [\cdot] e {\xi;v}$ iff $\reduce c {(v_1,u)}$ and if so
%\item $\dom \xi \vdash v \vsplito [v_1,v_2]$
%\item $\reify \xi {v_2} q$
%\item $q \equiv (\letin{l}{u}{r}) : A_2$
%\end{itemize}
%\end{theorem}
%
%\subsubsection{\bbone-Dependent Types}
%\begin{theorem}
%If $\cdot\vdash e : A \splitonesym [c,l:\tau.r]$ then,
%\begin{itemize}
%\item $\typesone [\cdot] e A$ 
%\item $A \tsplito [A_1,a.A_2]$
%\item $\types [\cdot] c {A_1 \times \tau}$ and $\types [l:\tau,a:A_1] r A_2$ 
%\item $\diaone [\cdot] e {\xi;v}$ iff $\reduce c {(v_1,u)}$ and if so
%\item $\dom \xi \vdash v \vsplito [v_1,v_2]$
%\item $\reify \xi {v_2} q$
%\item $q \equiv (\letin{l}{u}{r}) : A_2$
%\end{itemize}
%\end{theorem}

\input{figures/splitting-misc}
